An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Section 4 cleanup; Psi explanation

The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
\bo{Maybe cite prop in the appendix}
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
We show\bo{cite lemma} that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
Now enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving this is well-defined uses a chain of arguments involving the Bayes risk\bo{characterization prop in appendix, ...}, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
Let $\U$ contain all optimal report sets $U$ of the form above.

@@

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
\jessie{It might help to say something like: initialize a \emph{potential link} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$, or something to explain what $\Psi$ is?  (Note sure how to phrase it.)}
\raf{Agreed; probably best to just describe what $\Psi$ will represent before giving the construction.}

@@

\begin{proof}[Sketch]
  (See Appendix~\ref{app:calibration} for the full proof.)
  \emph{Well-defined:}
  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.

>>>>

\bo{Removed comments to point to appendix, since that creates more links...}
Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
We show that as we vary $p$ over the infinite $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \langle p, L(u) \rangle$.
Associate each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$.
Now enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

Intuitively, to create separation, we just need to ``thicken'' this construction by mapping all approximately-optimal points $u$ to optimal reports $r$.
Let $\U$ contain all optimal report sets $U$ of the form above.
A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.

@@

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}

@@

\begin{proof}[Sketch]
  \emph{Well-defined:}
  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.
